Price of Anarchy for Mean Field Games

### 2018-08-01 PoA.tex
almost finished with lemma 1

	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then inequalities (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give for $b_2 \geq b_2^*$:
	\begin{equation*}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c/2}=\frac{4\epsilon}{c}.
	\end{equation*}
	Since the proof holds for arbitrary $\epsilon>0$, and $c=\sqrt{(q+\bar{q}(1-s)^2)(r+\bar{r}(1-\bar{s})^2)}>0$ is independent of $b_2$ and $\epsilon$, we conclude:
	\begin{equation*}
		\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0, 
	\end{equation*}
	and thus,
	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$

@@

\begin{proof}
	First, we show that for $t\in[0,T)$: (ToDo: This is already stated in Proposition 4.)
	$$\lim_{b_2 \to \infty}b_2\eta^{b_2}_t=(r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}}=\sqrt{(r+\bar{r})(q+\bar{q})} =: c_\eta.$$
	And thus, there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$:
	$$b_2\eta^{b_2}_0 \leq c_\eta+\frac{1}{2}.$$
	Clearly there exists $b_2^{*,2}$ such that for $b_2 \geq b_2^{*,2}$:
	$$b_2\eta^{b_2}_T=b_2D^\eta=b_2(q_T+\bar{q}_T)\geq c_\eta+2.$$
	Since $\lim_{b_2 \to \infty} B^\eta (D^\eta)^2+2A^\eta D^\eta-C^\eta=\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists $b_2^{*,3}$ such that for $b_2 \geq b_2^{*,3}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing. Since for any $b_2$, the function $t \mapsto b_2 \eta^{b_2}_t$ is continuous, by the intermediate value theorem we have for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, there exists a $t^*_{b_2}\in[0,T]$ such that:
	$$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1$$
	and:
	$$b_2 \eta^{b_2}_t \leq c_\eta+1,\ \forall t\leq t^*_{b_2}.$$
	Thus,
	$$1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta=\frac{\frac{1}{b_2} \left[ToDO \right]}{\frac{1}{b_2^2} \left[ToDo \right]}-c_\eta=\frac{ToDo}{ToDo}.$$
	After rearranging terms:
	\begin{equation}
	\begin{split}
	\frac{D}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
	&= \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta)+ToDo \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t)} \\
	&\leq  \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t)}.
	\end{split}
	\label{eq:lemma_1}
	\end{equation}
	Since we have: (ToDo: show these limits)
	$$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right) =0,$$
	there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$, we have:
	$$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$$
	and thus returning to inequality (\ref{eq:lemma_1}), for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4} \}$:
	$$\frac{D^\eta}{2(r+\bar{r})}\leq \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}, $$
	$$e^{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}\leq -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) , $$
	$$\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})\leq ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right) , $$
	\begin{equation}
	b_2(T-t^*_{b_2})\leq \frac{1}{\frac{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)}{b_2}} ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right).
	\label{eq:lemma_2}
	\end{equation}
	Since $\lim_{b_2 \to \infty}\frac{\delta^{+,b_2}_\eta}{b_2}=c_{\delta_\eta^{b_2 \to \infty}}=-\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2}$, there exists $b_2^{*,5}$ such that for $b_2 \geq b_2^{*,5}$:
	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{\delta^{+,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2}, $$
	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2},$$
	and thus,
	$$c_{\delta_\eta^{b_2 \to \infty}} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta^{b_2 \to \infty}}.$$	
	Returning to equation (\ref{eq:lemma_2}), for $b_2 \geq b_2^{*,l}:=\max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4},b_2^{*,5}\}$:
	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right).$$
	Finally, for $b_2 \geq b_2^{*,l}$, we have:
	\begin{equation*}
	\begin{split}
	\int_0^T b_2 \eta^{b_2}_t dt&=\int_0^{t^*_{b_2}} b_2 \eta^{b_2}_t dt+\int_{t^*_{b_2}}^T b_2 \eta^{b_2}_t dt \\
	&\leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta\\
	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right)=:M.	
	\end{split}
	\end{equation*}

>>>>

	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then inequalities (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give for $b_2 \geq b_2^*$:
	\begin{equation*}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c/2}=\frac{4\epsilon}{c}.
	\end{equation*}
	Since the proof holds for arbitrary $\epsilon>0$, and $c=\sqrt{(q+\bar{q}(1-s)^2)(r+\bar{r}(1-\bar{s})^2)}>0$ is independent of $b_2$ and $\epsilon$, we conclude:
	\begin{equation*}
		\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0, 
	\end{equation*}
	and thus,
	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$\\

@@

\begin{proof}
	First, we show that for $t\in[0,T)$: (ToDo: This is already stated in Proposition 4.)
	$$\lim_{b_2 \to \infty}b_2\eta^{b_2}_t=(r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}}=\sqrt{(r+\bar{r})(q+\bar{q})} =: c_\eta.$$
	And thus, there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$:
	$$b_2\eta^{b_2}_0 \leq c_\eta+\frac{1}{2}.$$
	Clearly there exists $b_2^{*,2}$ such that for $b_2 \geq b_2^{*,2}$:
	$$b_2\eta^{b_2}_T=b_2D^\eta=b_2(q_T+\bar{q}_T)\geq c_\eta+2.$$
	Since $\lim_{b_2 \to \infty} B^\eta (D^\eta)^2+2A^\eta D^\eta-C^\eta=\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists $b_2^{*,3}$ such that for $b_2 \geq b_2^{*,3}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing. Since for any $b_2$, the function $t \mapsto b_2 \eta^{b_2}_t$ is continuous, by the intermediate value theorem we have for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, there exists a $t^*_{b_2}\in[0,T]$ such that:
	$$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1$$
	and:
	$$b_2 \eta^{b_2}_t \leq c_\eta+1,\ \forall t\leq t^*_{b_2}.$$
	Thus,
	\begin{equation*}
	\begin{split}
	1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta&=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} \right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}}-c_\eta,
	\end{split}
	\end{equation*}
	$$
	1=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}-c_\eta \left(\frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2}\right)+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -c_\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right)\right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}}.
	$$

	After rearranging terms:
	\begin{equation}
	\begin{split}
	\frac{D^\eta}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
	&= \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta)+ToDo \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})} \\
	&\leq  \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.
	\end{split}
	\label{eq:lemma_1}
	\end{equation}
	Since we have: (ToDo: show these limits)
	$$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right) =0,$$
	there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$, we have:
	$$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$$
	and thus returning to inequality (\ref{eq:lemma_1}), for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4} \}$:
	$$\frac{D^\eta}{2(r+\bar{r})}\leq \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}, $$
	$$e^{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}\leq -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) , $$
	$$\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})\leq \ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right) , $$
	\begin{equation}
	b_2(T-t^*_{b_2})\leq \frac{1}{\frac{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)}{b_2}} \ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right).
	\label{eq:lemma_2}
	\end{equation}
	Since $\lim_{b_2 \to \infty}\frac{\delta^{+,b_2}_\eta}{b_2}=c_{\delta_\eta^{b_2 \to \infty}}=-\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2}$, there exists $b_2^{*,5}$ such that for $b_2 \geq b_2^{*,5}$:
	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{\delta^{+,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2}, $$
	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2},$$
	and thus,
	$$c_{\delta_\eta^{b_2 \to \infty}} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta^{b_2 \to \infty}}.$$	
	Returning to equation (\ref{eq:lemma_2}), for $b_2 \geq b_2^{*,l}:=\max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4},b_2^{*,5}\}$:
	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right).$$
	Finally, for $b_2 \geq b_2^{*,l}$, we have:
	\begin{equation*}
	\begin{split}
	\int_0^T b_2 \eta^{b_2}_t dt&=\int_0^{t^*_{b_2}} b_2 \eta^{b_2}_t dt+\int_{t^*_{b_2}}^T b_2 \eta^{b_2}_t dt \\
	&\leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta\\
	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right)=:M.	
	\end{split}
	\end{equation*}
\end{proof}
